Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Start implementing Peter's comments

\subsection{Planning problems}
\subsubsection{Classical Planning problems. } Planning is the process of computing several steps of a problem-solving procedure before executing any of them. In classical planning problems the environment is assumed to \emph{deterministic, observable and state}. Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics. The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.

\subsubsection{Probabilistic Planning problems}
Real-World applications are far from deterministic, induced by natural dynamics and chance. To accommodate for Real-World domains probabilistic planning problems were introduced.  These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty. Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.

\subsection{Problem domains}
\subsubsection{Goal-oriented MDPs. }The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL). PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}. These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$. $\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.

>>>>

\subsection{Planning problems}

Planning is the process of computing several steps of a problem-solving procedure before executing any of them.

\subsubsection{Classical Planning problems.}

A classical planning problem is defined as states, actions, conditions and a goal state and are solved using search and can be aided using heuristics. The environment is assumed to be \emph{deterministic, observable and static}. The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.

\subsubsection{Probabilistic Planning problems}

Real-World applications are far from deterministic, induced by natural dynamics and chance. To accommodate for Real-World domains probabilistic planning problems were introduced.  These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty. Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online, while executing the plan, or offline, where all possibilities is calculated upfront.

\subsection{Problem domains}

\subsubsection{Goal-oriented MDPs. }The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL). PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}. These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$. $\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
